Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex

We rendered a feature for each position covered, and set its value to be the
word at that position.

We also used NLTK's part of speech tagger to tag the context, and included those
as we did the literal words in the feature set.  This was trained on NLTK's
\verb+maximum entropy treebank pos tagger+ data, which is included with the NLTK
package.

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{baseline}
\caption{\label{fig:base}Baseline scores for our two baseline systems}
\end{figure}

@@

%\begin{figure}[H]
%\includegraphics[width=\textwidth]{pg_0001}
%\caption{\label{fig1}}
%\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{pg_0002}
%stepwise graph 1
%classifiert, collocation, cooccurrence  
%Interpret this graph
\caption{\label{fig2}}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{pg_0003}
\caption{\label{fig3}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}The scores of systems with colocation window between 2 and 4, cooccurrence handling on, \naive{} Bayes classifier and dependency parsing off are presented here. Each plotted number corresponds to a system, and the number refers to the colocation window}
\end{figure}

@@

\subsubsection{Collocation}

>>>>

We rendered a feature for each position covered, and set its value to be the
word at that position. We also used NLTK's part of speech tagger to
tag the context, and included those as we did the literal words in the
feature set.  This was trained on NLTK's
\verb+maximum entropy treebank pos tagger+ data, which is included
with the NLTK package.

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{baseline}
\caption{\label{fig:base}Baseline scores for our two baseline systems}
\end{figure}

@@

%\begin{figure}[h]
%\includegraphics[width=\textwidth]{pg_0001}
%\caption{\label{fig1}}
%\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{pg_0002}
%stepwise graph 1
%classifiert, collocation, cooccurrence  
%Interpret this graph
\caption{\label{fig2}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{pg_0003}
\caption{\label{fig3}}
\end{figure}

According to Figure \ref{fig3}, when the base word feature vector was
enabled and the dependency parsing was disabled, the \naive{} Bayes
classifier improved in performance. On the other hand, the performance
of the Decision Tree classifier seems to be independent of the base
word and dependency parsing features.

\begin{figure}
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}The scores of systems with colocation window between 2 and 4, cooccurrence handling on, \naive{} Bayes classifier and dependency parsing off are presented here. Each plotted number corresponds to a system, and the number refers to the colocation window}
\end{figure}

@@
